---
output:
  pdf_document: default
  html_document: default
editor_options: 
  chunk_output_type: console
---
# exercise 3

# 3.2.5.
Q1. In a single pipeline for each condition, find all flights that meet condition:

A1. Use filter() to code each conditions. 
-Had an arrival delay of two or more hours (arr_delay >=120)
```{r}
flights |> filter(arr_delay >= 120)
```

-Flew to Houston (IAH or HOU) (dest == "IAH" | dest == "HOU")
```{r}
flights |> filter(dest == "IAH" | dest == "HOU")
```

-Were operated by United, American, or Delta (carrier %in% c("UA", "AA", "DL"))
```{r}
flights |> filter(carrier %in% c("UA", "AA", "DL"))
```

-Departed in summer (month %in% c(7, 8, 9))
```{r}
flights |> filter(month %in% c(7, 8, 9))
```

-Arrived more than two hours late but didn't leave late (arr_delay > 120 & dep_delay <= 0) 
```{r}
flights |> filter(arr_delay > 120 & dep_delay <= 0)
```

-Were delayed by at least an hour, but made up over 30 minutes in flight (dep_delay >= 60 & dep_delay - arr_delay >= 30)
```{r}
flights |> filter(dep_delay >= 60 & dep_delay - arr_delay >= 30)
```

Q2. Sort flights to find the flights with the longest departure delays. Find the flights that left earliest in the morning.

A2. 
Sorting flights that had the longest departure delays. The first result is the one we are looking for.
```{r}
flights |> arrange(desc(dep_delay))
```

Sorting flights that left earliest in the morning
Use 'time_hour' & find the earliest schedule in the morning (5 A.M.)
# from https://rdrr.io/cran/nycflights13/man/flights.html)

```{r}
flights |> arrange(time_hour)
```
Q3. Sort flights to find the fastest flights.
A3. The velocity of the flight can be calculated by dividing the distance by time
```{r}
flights |> arrange(desc(distance/air_time))
```

Q4. Was there a flight on everyday of 2013?
A4. Use distinct() to remove duplicate rows of month and day, and check if there is a missing day. Thankfully, there are 365 rows meaning that flights were on everyday.
```{r}
flights |> distinct(month, day)
```
Q5. Which flights traveled the farthest distance? Which traveled the least distance?
A5. 
Finding the flight that traveled the farthest distance
It was the flights from JFK to HNL with the distance of 4983 miles. (N380HA, N384HA, N381HA, N385HA, N389HA, etc) 
```{r}
flights |> arrange(desc(distance))
```

Finding the flight that traveled the least distance
It is a flight from EWR to LHA with the distance of 17 miles.
```{r}
flights |> arrange(distance)
```
Q6. Does it matter what order you used filter() and arrange() if you're using both? Why/Why not? Think about the results and how much work the functions would have to. 
## challenging..

A6. 'fliter' comes first vs. 'arrange' comes first
'filter' sorts out rows with specific conditions, and 'arrange' gives order of the rows with specific conditions
I think the using both commands with different orders would make no difference because they have separate roles.
For example, we can test if the result is same in.. 
filter(arrange(distance)) vs. arrange(filter(distance))

case 1. filter comes first
```{r}
flights |> filter(month == 1)
flights |> arrange(distance)
```

case 2. arrange comes first
```{r}
flights |> arrange(distance)
flights |> filter(month == 1)
```

# 3.3.5
Q1. Campare dep_time, sched_dep_time, and dep_delay. How would you expect those three numbers to be related?
A1. I think dep_delay = dep_time - scjed_dep_time. 


Q2. Brainstorm as many ways as possible to select dep_time, dep_delay, arr_time, and arr_delay from flights.
A2.
```{r}
flights |> select(dep_time, dep_delay, arr_time, arr_delay)
```

```{r}
flights |> select(starts_with("dep") | starts_with("arr"))
```
```{r}
flights |> select(dep_time:arr_delay, -contains("sched"))
```
```{r}
flights |> select(ends_with("time") | ends_with("delay"), -contains("sched"), -contains("air"))
```


Q3.  What happends if you specify the name of the same variable multiple times in a select() call?
A3. It only shows a one column for the repeated variable.
```{r}
flights |> select(dep_time, dep_time, dep_time)
```

Q4. What does the any_of() function do? Why might it be helpful in conjunction with this vector?
```{r}
variables <- c("year", "month", "day", "dep_delay", "arr_delay")
```

A4. According to the link below, 'any_of()' function selects variables that are contained in a character vector. 
# Refer to https://tidyselect.r-lib.org/reference/all_of.html
Using 'all_of()' with the conjunction, we can get table with 5 columns that are included in the conjunction. 

```{r}
variables <- c("year", "month", "day", "dep_delay", "arr_delay")
flights |> select(all_of(variables))
```

Q5. Does the result of running the following code surprise you? How do the select helpers deal with upper and lower case by default? How can you change that default?

```{r}
flights |> select(contains("TIME"))
```

A5. I was surprised at the result because I expected to see error with the upper case. We can modify helpers 'ignore.case' from default value of "TRUE" to "FALSE". Then, the commands deal with the upper and lower case.
```{r}
flights |> select(contains("TIME", ignore.case = FALSE))
```

Q6. Rename air_time to air_time_min to indicate units of measurement and move it to the beginning of the data frame.
A6.
```{r}
flights |> rename(air_time_min=air_time) |> relocate(air_time_min, .before=year)
```

Q7. Why doesn't the following work, and what does the error mean?
```{r}
flights |> select(tailnum) |> arrange(arr_delay)
```

A7. The error means there is no 'arr_delay' column to arrange the order. This is because we have removed all columns except 'tailnum' when the command 'select(tailnum)' is exercised. After the command, there is no variable for the second command.
```{r}
flights |> select(tailnum)
```

# 3.5.7.
Q1. Which carrier has the worst average delays? Challenge: can you disentangle the effects of bad airports vs. bad carriers? Why/Why not?  
#challenging

A1. It is F9. with 20.2 average delay.
```{r}
flights |> group_by(carrier) |> summarize(avg_delay = mean(dep_delay, na.rm=TRUE)) |> arrange(desc(avg_delay))
```

To disentangle the effects of bad airports vs. bad carriers
```{r}
flights |> group_by(carrier, dest) |> summarize(avg_delay=mean(dep_delay, na.rm=TRUE), n()) |> arrange(desc(n()))
```



Q2. Find the flights that are most delayed upon departure from each destination.
A2. 
```{r}
flights |> group_by(dest) |> slice_max(n=1, order_by = dep_delay, na_rm = TRUE) |> select(dest, flight, origin, dep_delay, month, day) |> arrange(desc(dep_delay), desc(flight))
``` 


Q3. How do delays vary over the course of the day? Illustrate your answer with a plot.
A3.
```{r}
flights |> group_by(sched_dep_time) |> summarize(avg_delay = mean(dep_delay, na.rm = TRUE)) |> mutate(hour = sched_dep_time %/% 100, minute = sched_dep_time %% 100) |> mutate(time_hr = hour + minute/60) |> mutate(time_hr = hour + minute/60) |> ggplot(aes(x=time_hr, y=avg_delay)) + geom_line() + geom_smooth(color="red", se=FALSE)
```



Q4. What happens if you supply a negative n to slice_min() and friends?
A4.
```{r}
flights |> filter(origin == "JFK") |> group_by(dest) |> summarize(avg_delay=mean(dep_delay, na.rm=TRUE)) |> arrange(desc(avg_delay)) |> slice_min(avg_delay, n=3)
```

# A tibble: 3 × 2
  dest  avg_delay
  <chr>     <dbl>
1 PSP       -2.94
2 STT        3.74
3 SRQ        4.43

```{r}
flights |> filter(origin == "JFK") |> group_by(dest) |> summarize(avg_delay=mean(dep_delay, na.rm=TRUE)) |> arrange(desc(avg_delay)) |> slice_min(avg_delay, n=-3)
```

# A tibble: 67 × 2
   dest  avg_delay
   <chr>     <dbl>
 1 PSP       -2.94
 2 STT        3.74
 3 SRQ        4.43
 4 HNL        4.90
 5 JAC        5   
 6 ACK        6.46
 7 BQN        6.67
 8 BHM        7   
 9 MVY        7.05
10 SLC        7.73
# ℹ 57 more rows
# ℹ Use `print(n = ...)` to see more rows

It prints 60-3=57 rows, not the three rows. When the value of n becomes negative, it works to subtract the total number of rows.

Q5. Explain what count() does in terms of the dplyr verbs you just learned. What does the sort argument to count() do?
A5. It count the frequency of the variables in the data set. For example, count(species) shows the column of species and the number of each species.The sort argument shows the largest groups at the top. 


Q6. Supporse we have the following tiny data frame.

```{r}
df <- tibble( x=1:5, y=c("a", "b", "a", "a", "b"), z=c("K", "K", "L", "L", "K"))
```
X Y Z
1 a K
2 b K
3 a L
4 a L
5 b K

a) Write down what you think the output will look like, then check if you were correct, and describe what group_by() does.
```{r}
df |> group_by(y)
```
Expectation: There would be two groups "a" and "b". 
Result:
# A tibble: 5 × 3
# Groups:   y [2]
      x y     z    
  <int> <chr> <chr>
1     1 a     K    
2     2 b     K    
3     3 a     L    
4     4 a     L    
5     5 b     K   

b) Write down what you think the output will look like, then check if you were correct, and describe what arrange() does. Also, comment on how it's different from the group_by() in a part (a).
```{r}
df |> arrange(y)
```
Expectation: a comes first and b comes later.
X Y Z
1 a K
3 a L
4 a L
2 b K
5 b K

# A tibble: 5 × 3
      x y     z    
  <int> <chr> <chr>
1     1 a     K    
2     3 a     L    
3     4 a     L    
4     2 b     K    
5     5 b     K    



c) Write down what you think the output will look like, then check if you were correct, and describe what the pipeline does.
```{r}
df |> group_by(y) |> summarize(mean_x = mean(x))
```
Expectation: mean_x= (1+3+4)/3=2.67 for a, (2+5)/2=3.5 for b
Result: 
# A tibble: 2 × 2
  y     mean_x
  <chr>  <dbl>
1 a       2.67
2 b       3.5 

d) Write down what you think the output will look like, then check if you were correct, and describe what the pipeline does. Then, comment on what the message says.
```{r}
df |> group_by(y,z) |> summarize(mean_x=mean(x))
```
Expectation: Groups would be (a,K), (a,L), (b,K)
mean_x= 1 for (a,K), (3+4)/2=3.5 for (a,L), (2+5)/2=3.5 for (b,K)
Result:
# A tibble: 3 × 3
# Groups:   y [2]
  y     z     mean_x
  <chr> <chr>  <dbl>
1 a     K        1  
2 a     L        3.5
3 b     K        3.5


e) Write down what you think the output will look like, then check if you were correct, and describe what the pipeline does. How is the output different from the one in part (d)?
```{r}
df |> group_by(y, z) |> summarize(mean_x=mean(x), .groups = "drop")
```
Expectation: .groups="drop" undo the grouping. The pipe gives sequence of commands, meaning following command would work after the previous command are finished. Therefore, the above means "first, group by the combination of y and z. Next, summarize the mean value of x and undo the grouping of y." The result woule show the same output in part (d) because still there are three groups (a,K), (a,L), and (b,K) regardless of y group.
Result:
# A tibble: 3 × 3
  y     z     mean_x
  <chr> <chr>  <dbl>
1 a     K        1  
2 a     L        3.5
3 b     K        3.5


f) Write down what you think the output will look like, then check if you were correct, and describe what each pipeline does. How are the outputs of the two pipelines different?

```{r}
df |> group_by(y, z) |> summarize(mean_x=mean(x))
```
Expectation: Groups would be (a,K), (a,L), (b,K)
mean_x= 1 for (a,K), (3+4)/2=3.5 for (a,L), (2+5)/2=3.5 for (b,K)
Result:
# A tibble: 3 × 3
# Groups:   y [2]
  y     z     mean_x
  <chr> <chr>  <dbl>
1 a     K        1  
2 a     L        3.5
3 b     K        3.5


```{r}
df |> group_by(y, z) |> mutate(mean_x=mean(x))
```
Expectation: I guessed it would be the same because mutate command creates new value and it is already in the former table.
Result:
# A tibble: 5 × 4
# Groups:   y, z [3]
      x y     z     mean_x
  <int> <chr> <chr>  <dbl>
1     1 a     K        1  
2     2 b     K        3.5
3     3 a     L        3.5
4     4 a     L        3.5
5     5 b     K        3.5   

However, the table here is different from the former one. It shows x value, representing additional values of (4,a,L) and (5,b,K) which were erased before as overlapping. 

